%-----------------------------------------------------------------------------------------------------------------------------------------------%
%   The MIT License (MIT)
%
%   Customized CV for Muzammil Hussain based on template by Jitin Nair
%-----------------------------------------------------------------------------------------------------------------------------------------------%

\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%   PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{supertabular}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[unicode, draft=false]{hyperref}
\usepackage{fontawesome5}

\newcolumntype{C}{>{\centering\arraybackslash}X} 
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & &  #2 \\
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & &  #2 \\
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%   TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{} }
\Huge{Muzammil Hussain} \\[7.5pt]
United Kingdom $|$ 
\href{tel:+447473426326}{\raisebox{-0.05\height}\faMobile\ 07473426326} $|$ 
\href{mailto:muzammilfive@gmail.com}{\raisebox{-0.05\height}\faEnvelope\ muzammilfive@gmail.com} $|$ 
\href{https://linkedin.com/in/muzammilhussain5}{\raisebox{-0.05\height}\faLinkedin\ linkedin.com/in/muzammilhussain5} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%   SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
Software Engineer with 3 years of experience building scalable and secure web applications using Java, Kotlin, TypeScript, Spring Boot, and React. Demonstrated expertise in designing microservices, developing reusable components, and improving system performance. Effective team player in agile environments, focused on code quality and user experience.

%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{joblong}{Software Engineer (Consultant), Goldman Sachs}{Sep 2024 -- Present, Birmingham, UK}
\item Modernized a Treasury Reporting tool by redesigning the UI/UX and building a SPA using ReactJS in a micro-frontend architecture supported by Spring Boot backend.
\item Migrated TQuest (historical transaction query tool backed by Elasticsearch) to a JWT-based Ping Federate authentication system, strengthening authorization, compliance, and secure coding practices.
\item Analysed 80 APIs to ensure regulatory compliance, data privacy, and access controls to PII-classified datastores.
\item Remediated 10+ security vulnerabilities (SQL Injection, XSS, hard-coded secrets, RCE), aligning with secure coding and DevOps best practices.
\end{joblong}

\begin{joblong}{Full Stack Developer, DBS Bank}{Mar 2022 -- Sep 2022, Hyderabad, IN}
\item Contributed to end-to-end development of new features such as Multiple Booking Locations, enabling cross-country corporate loans to be processed within a single case file.
\item Owned and maintained 4 Kotlin/Java Spring Boot microservices, enforcing TDD and peer reviews.
\item Optimized PAW Dashboard performance by 60\% using backend pagination, Kotlin coroutines, and REST API optimization.
\item Built 50+ reusable TypeScript Web Components (Lit framework), enhancing modularity and frontend consistency.
\item Implemented batch processing with Spring Batch to automate database records cleanup tasks.
\end{joblong}

\begin{joblong}{Application Developer, DBS Bank}{Sep 2020 -- Feb 2022, Hyderabad, IN}
\item Designed and delivered an @User Tagging component with authorization checks, debounced search, and contextual notifications.
\item Achieved 80\%+ test coverage by writing JUnit & Mockito unit tests under TDD.
\item Implemented region-specific S3 bucket storage for documents, ensuring compliance with data localisation policies.
\item Conducted peer code reviews and regression testing, ensuring CI/CD pipeline quality.
\item Partnered with cross-functional teams and business stakeholders to gather requirements, estimate user stories, and deliver client-centric features.
\end{joblong}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}} 	
Jan 2024 & MSc Advanced Computer Science, \textbf{University of Leicester}, UK \\
Sep 2020 & Bachelors in Information Technology, \textbf{Gokaraju Rangaraju Institute of Engineering \& Technology}, IN \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%   SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Languages & Kotlin, Java, Go, TypeScript/JavaScript, SQL \\
Frameworks & Spring Boot, ReactJS, Lit Elements, Web Components, JUnit, Mockito, Jest \\
Architecture & Microservices, Micro-frontend, SPA, Agile/XP (TDD, Pair Programming, Iterative Development) \\
DevOps & Tools & CI/CD (Jenkins, GitLab), AWS S3, PCF, Git, Bitbucket, Splunk, Postman, Nginx, MariaDB \\
Security & Compliance & Spring Security, OAuth 2.0, JWT, Secure Coding (XSS, SQL Injection prevention) \\
Other & JSON, XML, Web Accessibility, HTML, CSS \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%   PROJECTS
%----------------------------------------------------------------------------------------
\section{Relevant Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Property Rental Hub} & \hfill University of Leicester (Dissertation, Jun 2023 -- Sep 2023) \\
\multicolumn{2}{@{}X@{}}{Responsive property rental application with microservices backend (Spring). Features: Google Maps API integration, JWT authentication with HTTPS cookies, property management and bookings.} \\
\end{tabularx}

\vspace{5pt}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Connect Match Puzzle Game} & \hfill University of Leicester (Dec 2022) \\
\multicolumn{2}{@{}X@{}}{Web-based puzzle game built with React and Redux, implementing Depth-First Search (DFS) to reveal potential pathways between tiles.} \\
\end{tabularx}

\vspace{5pt}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{House Price Prediction (NYC)} & \hfill University of Leicester (Mar 2023) \\
\multicolumn{2}{@{}X@{}}{Built predictive model with 95\% accuracy using linear regression. Applied preprocessing including standardization, outlier removal, and dimensionality reduction.} \\
\end{tabularx}
\vfill
\center{\footnotesize Last updated: \today}

\end{document}
